Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-09-29 draft.tex
stuff

>>>>

\begin{figure}
    \centering
    \begin{tabular}{c}\begin{tikzpicture}
        \coordinate (O) at (0, 0);
        \coordinate (A) at ({cos(0)}, {sin(0)});
        \coordinate (B) at ({cos(60)}, {sin(60)});
        \coordinate (C) at ({cos(120)}, {sin(120)});
        \coordinate (D) at ({cos(180)}, {sin(180)});
        \coordinate (E) at ({cos(240)}, {sin(240)});
        \coordinate (F) at ({cos(300)}, {sin(300)});
        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
        \draw[dashed] (O) -- (A); \draw[dotted] (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
    \end{tikzpicture}\\ (1) \end{tabular}
    \begin{tabular}{c}\begin{tikzpicture}
        \coordinate (O) at (0, 0);
        \coordinate (A) at ({cos(0)}, {sin(0)});
        \coordinate (B) at ({cos(60)}, {sin(60)});
        \coordinate (C) at ({cos(120)}, {sin(120)});
        \coordinate (D) at ({cos(180)}, {sin(180)});
        \coordinate (E) at ({cos(240)}, {sin(240)});
        \coordinate (F) at ({cos(300)}, {sin(300)});
        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
        \draw[dotted] (A) -- (B); \draw (B) -- (C) -- (D) -- (E) -- (F) -- (A);
        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
    \end{tikzpicture}\\ (2) \end{tabular}
    \begin{tabular}{c}\begin{tikzpicture}
        \coordinate (O) at (0, 0);
        \coordinate (A) at ({cos(0)}, {sin(0)});
        \coordinate (B) at ({cos(60)}, {sin(60)});
        \coordinate (C) at ({cos(120)}, {sin(120)});
        \coordinate (D) at ({cos(180)}, {sin(180)});
        \coordinate (E) at ({cos(240)}, {sin(240)});
        \coordinate (F) at ({cos(300)}, {sin(300)});
        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw[dotted] (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
    \end{tikzpicture}\\ (3) \end{tabular}
    \begin{tabular}{c}\begin{tikzpicture}
        \coordinate (O) at (0, 0);
        \coordinate (A) at ({cos(0)}, {sin(0)});
        \coordinate (B) at ({cos(60)}, {sin(60)});
        \coordinate (C) at ({cos(120)}, {sin(120)});
        \coordinate (D) at ({cos(180)}, {sin(180)});
        \coordinate (E) at ({cos(240)}, {sin(240)});
        \coordinate (F) at ({cos(300)}, {sin(300)});
        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw[dotted] (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
    \end{tikzpicture}\\ (4) \end{tabular}
    \caption{Examples and counterexamples for building a manifold-like $1$-patching of a $2$-dimensional manifold-like triangulation. 
    (1) We have already added the edge patch along the dashed line and we add the edge patch along the dotted line.
    (2) The new edge patch may already be a subset of the subtriangulation
    (3) An inadmissible choice because the new edge patch has no overlap with current subtriangulation, though the next subtriangulation would be manifold-like
    (4) An inadmissible choice because the new edge patch has no overlap with current subtriangulation and the next subtriangulation would not be manifold-like.}\label{figure:illustrationpatching}
\end{figure}

% \begin{figure}
%     \centering
%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
%         \coordinate (O) at (0, 0);
%         \coordinate (A) at ({0.8*cos(  0)}, {0.8*sin(  0)});
%         \coordinate (B) at ({0.8*cos(120)}, {0.8*sin(120)});
%         \coordinate (C) at ({0.8*cos(240)}, {0.8*sin(240)});
%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
%         \draw (A) -- (B) -- (C) -- cycle; \draw (X) -- (Y) -- (Z) -- cycle;
%         \draw[fill=gray!20] (X) -- (Y) -- (B) -- cycle;
%         \draw[fill=gray!20] (Y) -- (Z) -- (C) -- cycle;
%         \draw[fill=gray!20] (Z) -- (X) -- (A) -- cycle;
%         \draw[fill=gray!20] (A) -- (X) -- (B) -- cycle;
%         \draw[fill=gray!20] (B) -- (Y) -- (C) -- cycle;
%         \draw[fill=gray!20] (C) -- (Z) -- (A) -- cycle;
%     \end{tikzpicture}\\ (1) \end{tabular}
%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
%         \coordinate (O) at (0, 0);
%         \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
%         \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
%         \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
%         \draw (O) -- (A);
%         \draw (O) -- (B);
%         \draw (O) -- (C);
%         \draw (O) -- (X);
%         \draw (O) -- (Y);
%         \draw (O) -- (Z);
%         %
%     \end{tikzpicture}\\ (2) \end{tabular}
%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
%         \tikzset{z={(90:1cm)}, y={(-30:1cm)}, x={(210:1cm)}}
%         % \tikzset{z={(90:1cm)}, y={(-10:1cm)}, x={(250:1cm)}}
% 
%         \coordinate (O) at (0, 0);
%         \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
%         \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
%         \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
%         \coordinate (T) at ({0}, {0}, {3});
% 
%         \draw[thick, fill=gray!30] (O) -- (C) -- (T) -- cycle;
%         \draw[thick, fill=gray!30] (O) -- (Y) -- (T) -- cycle;
%         \draw[thick, fill=gray!30] (O) -- (Z) -- (T) -- cycle;
%         \draw[thick, fill=gray!30] (O) -- (A) -- (T) -- cycle;
%         \draw[thick, fill=gray!30] (O) -- (B) -- (T) -- cycle;
%         \draw[thick, fill=gray!30] (O) -- (X) -- (T) -- cycle;
% 
%     \end{tikzpicture}\\ (3) \end{tabular}
%     \caption{Example of a connected $2$-dimensional manifold triangulation, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
% \end{figure}
